Perspective simulation

### 2021-02-22 scripts/r/simulations/simulations.Rmd
:memo: - start factors model

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(rmdformats)
library(tidyverse)
theme_set(theme_light())
library(patchwork)
library(brms)
library(extraDistr)
library(HDInterval)
library(betapart)
library(summarytools)
my_seed <- 115116106
```

@@

# pop-level predictors
pop_pred <- lapply(replicate(n, list(rbinom(5, 1, 0.5))), at_least)
# group-level predictors
group_pred <- lapply(replicate(n, list(rbinom(5, 1, 0.5))), at_least)
# number of post-hoc changes to the measures
phoc_n <- rpois(n, 1)
# number of models run
mod_n <- sample(1:5, n, replace = T)
# major dimension
mdim <- sample(c("duration", "amplitude", "f0", "spectral", "other"), n, TRUE)
# temporal window
twin <- sample(c("segment", "syllable", "word", "phrase"), n, T)
# was data excluded?
excl <- rbinom(n, 1, 0.5)

@@

```{r eta-tbl}
# put together in a tibble
eta_tbl <- tibble(
  eta,
  se,
  team,
  pop_pred,
  pop_n = map(pop_pred, sum),
  group_pred,
  group_n = map(group_pred, sum),
  pop_sdi = sdi_mean(pop_pred),
  group_sdi = sdi_mean(group_pred),
  phoc_n,
  mod_n,
  mdim,
  twin,
  excl,
  exp,
  belf
)
```

@@

```{r meta-bm}
meta_bm <- brm(
  eta | se(se) ~
    (1 | team),
  data = eta_tbl,
  prior = priors,
  chain = 4,
  seed = my_seed,
  file = "./models/sim/meta_bm"
)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(rmdformats)
library(tidyverse)
theme_set(theme_light())
library(patchwork)
library(brms)
library(extraDistr)
library(HDInterval)
library(betapart)
# library(summarytools)
my_seed <- 115116106
```

@@

# pop-level predictors
pop_pred <- lapply(replicate(n, list(rbinom(5, 1, 0.5))), at_least)
# group-level predictors
group_pred <- lapply(replicate(n, list(rbinom(5, 1, 0.5))), at_least)
# number of post-hoc changes to the measures
phoc_n <- rpois(n, 1)
# number of models run
mod_n <- sample(1:5, n, replace = T)
# major dimension
mdim <- sample(c("duration", "amplitude", "f0", "spectral", "other"), n, TRUE)
# temporal window
twin <- sample(c("segment", "syllable", "word", "phrase"), n, T)
# was data excluded?
excl <- rbinom(n, 1, 0.5)
# reviewers' ratings
rating <- replicate(n, sample(0:100, sample(3:4, 1), replace = T))

@@

```{r eta-tbl}
# put together in a tibble
eta_tbl <- tibble(
  eta,
  se,
  team,
  pop_pred,
  pop_n = map(pop_pred, sum),
  group_pred,
  group_n = map(group_pred, sum),
  pop_sdi = sdi_mean(pop_pred),
  group_sdi = sdi_mean(group_pred),
  phoc_n,
  mod_n,
  mdim,
  twin,
  excl,
  rating,
  exp,
  belf,
  rating_mean = unlist(map(rating, mean)),
  rating_sd = unlist(map(rating, sd)),
  exp_mean = unlist(map(exp, mean)),
  exp_sd = unlist(map(exp, sd)),
  belf_mean = unlist(map(belf, mean)),
  belf_sd = unlist(map(belf, sd))
) %>%
  mutate(
  # need the following in cases where score = 0
  rating_mean = ifelse(rating_mean == 0, 0.01, rating_mean),
  exp_mean = ifelse(exp_mean == 0, 0.01, exp_mean),
  belf_mean = ifelse(belf_mean == 0, 0.01, belf_mean),
  # need the following in cases where there only one person in the team
  rating_sd = ifelse(is.na(rating_sd) | rating_sd == 0, 0.01, rating_sd),
  exp_sd = ifelse(is.na(exp_sd) | exp_sd == 0, 0.01, exp_sd),
  belf_sd = ifelse(is.na(belf_sd) | belf_sd == 0, 0.01, belf_sd)
)
```

@@

```{r meta-bm}
meta_bm <- brm(
  eta | se(se) ~
    (1 | team),
  data = eta_tbl,
  prior = priors,
  chain = 4,
  seed = my_seed,
  cores = 4,
  file = "./models/sim/meta_bm"
)
```

@@

# Factors analysis model

```{r factors-priors}
factors_priors <- c(
  prior(normal(0, 1), class = Intercept),
  prior(normal(0, 1), class = b),
  prior(normal(0, 1), class = meanme),
  prior(cauchy(0, 1), class = sdme),
  prior(lkj(2), class = corme)
)
```

```{r factors-bm}
factors_bm <- brm(
  eta | se(se) ~
    pop_sdi +
    phoc_n +
    mod_n +
    mdim +
    twin +
    excl +
    me(rating_mean, rating_sd) +
    me(exp_mean, exp_sd) +
    me(belf_mean, belf_sd),
  data = eta_tbl,
  prior = factors_priors,
  chain = 4,
  iter = 4000,
  control = list(max_treedepth = 15),
  seed = my_seed,
  cores = 4,
  file = "./models/sim/factors_bm"
)
```
